RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-12 paper.tex
working

There has been considerable work on specific techniques such as
social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV} that could benefit data scientists and deployment
specialists if they were made available, together, in a broader environment.

@@

Our work has been inspired by and has benefited from other recent projects
to improve data analysis environments and processes, including RStudio,
R packages such as Markdown, knitr and Shiny, and iPython notebooks,
to name a few. RStudio aims at providing an integrated development environment
for R programming, with support for publishing code in packages. Markdown,
knitR and Shiny provide R with sophisticated reporting capabilities, including
interactive web interfaces. IPython \cite{Perez:2007:IAS}
shares many of our goals...

@@

>>>>

There has been considerable work on specific techniques such as
social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV}
to support collaborative or social 
Our goal is to provide a productive environment in which such
techniques may be integrated and made available to a community.
Similarly, there are computational methods to support
high performance execution in an incremental code development
environment \cite{Guo:2010:TPI}.

@@

Our work has been inspired by and has benefited from other recent projects
to improve data analysis environments and processes, including RStudio,
R packages such as Markdown, knitr and Shiny \cite{CRAN}, and iPython notebooks,
to name a few. RStudio aims at providing an integrated development environment
for R programming, with support for publishing code in packages. Markdown,
knitR and Shiny provide R with sophisticated reporting capabilities, including
interactive web interfaces. IPython \cite{Perez:2007:IAS}
shares many of our goals...

@@

discussion about binding times, running vs.caching.
transparent vs. explicit operations done by programmers
